When does vapor pressure deficit drive or reduce evapotranspiration?

### 2017-12-13 doc/agu_2017/vpd.tex
done with slides, now jsut run through and maybe adjust figure linewidth, font and vpd to kpa

\begin{frame}{``Sign'' term as a function of VPD and PFT}
  \begin{figure}
    \begin{tikzpicture}
      \node[anchor=south west,inner sep=0] (image) at (0,0) {\adjincludegraphics[width=3.3in, trim={0 {0.51\height} 0 0}, clip]{fig05_pet.pdf}};
      \begin{scope}[x={(image.south east)},y={(image.north west)}]
        %% next four lines will help you to locate the point needed by forming a grid. comment these four lines in the final picture.↓
        % \draw[help lines,xstep=.1,ystep=.1] (0,0) grid (1,1);
        % \draw[help lines,xstep=.05,ystep=.05] (0,0) grid (1,1);
        % \foreach \x in {0,1,...,9} { \node [anchor=north] at (\x/10,0) {0.\x}; }
        % \foreach \y in {0,1,...,9} { \node [anchor=east] at (0,\y/10) {0.\y};}
        %% upto here
        % \draw[-latex, line width=2pt] (0.83,0.725) --++(0.0in,0.3in)node[anchor=south] {ET Increasing};
        % \draw[-latex, line width=2pt] (0.83,0.725) --++(0.0in,-0.3in)node[anchor=north] {ET Decreasing};
        % \draw[dashed,-latex, line width=5pt] (0.8,0.75) --++(0.0in,+0.5in)node[anchor=north] {ET Decreasing};
      \end{scope}
      % \node[align=center,red,font={\large}] at (image.southwest) {ET decreasing};
    \end{tikzpicture}
  \end{figure}
  \begin{textblock*}{0.25\textwidth}(0.02\textwidth,0.3\textheight)
    \textcolor{magenta}{Dashed line} gives response for potential evapotranspiration (PET).\\
    \medskip
    Plants are crucial for land response!
  \end{textblock*}
\end{frame}

@@

\begin{frame}{ideas}
  full summary statistics
  variance statistics
  joint distributions of LAI and VPD, and RH and esat
  aerodynamic scaling theory.
  put vpd in kpa
  add pictures to first slide
\end{frame}

@@

>>>>

\begin{frame}{``Sign'' term as a function of VPD and plant type}
  \begin{figure}
    \begin{tikzpicture}
      \node[anchor=south west,inner sep=0] (image) at (0,0) {\adjincludegraphics[width=3.3in, trim={0 {0.51\height} 0 0}, clip]{fig05_pet.pdf}};
      \begin{scope}[x={(image.south east)},y={(image.north west)}]
        %% next four lines will help you to locate the point needed by forming a grid. comment these four lines in the final picture.↓
        % \draw[help lines,xstep=.1,ystep=.1] (0,0) grid (1,1);
        % \draw[help lines,xstep=.05,ystep=.05] (0,0) grid (1,1);
        % \foreach \x in {0,1,...,9} { \node [anchor=north] at (\x/10,0) {0.\x}; }
        % \foreach \y in {0,1,...,9} { \node [anchor=east] at (0,\y/10) {0.\y};}
        %% upto here
        % \draw[-latex, line width=2pt] (0.83,0.725) --++(0.0in,0.3in)node[anchor=south] {ET Increasing};
        % \draw[-latex, line width=2pt] (0.83,0.725) --++(0.0in,-0.3in)node[anchor=north] {ET Decreasing};
        % \draw[dashed,-latex, line width=5pt] (0.8,0.75) --++(0.0in,+0.5in)node[anchor=north] {ET Decreasing};
      \end{scope}
      % \node[align=center,red,font={\large}] at (image.southwest) {ET decreasing};
    \end{tikzpicture}
  \end{figure}
  \begin{textblock*}{0.25\textwidth}(0.02\textwidth,0.3\textheight)
    \textcolor{magenta}{Dashed line} gives response for potential evapotranspiration (PET).\\
    \medskip
    Plants are crucial for land response!
  \end{textblock*}
\end{frame}

@@

\begin{frame}{Quantitative $VPD_{crit}$}

  \scriptsize
  \begin{table}
    \label{vpd_crit}
    \caption{Values of $VPD_{crit}$, where $\frac{\partial \; ET}{\partial \; VPD} = 0$, evaluated at PFT average values for $R_{air}$, $\sigma$, $\gamma$, and $c_s$. For reference, these values are also provided. For values of $VPD$ less than $VPD_{crit}$, $\frac{\partial \; ET}{\partial \; VPD}$ will be negative, and for values of $VPD$ greater than $VPD_{crit}$, $\frac{\partial \; ET}{\partial \; VPD}$ will be positive.}
    \centering
    \begin{tabular}{l c c c c c}
      \hline
      PFT & $R_{air}$ & $c_s$ (ppm) & $\gamma$ &  uWUE & \textbf{$VPD_{crit}$ (Pa)} \\
      \hline
      CRO &  288.680920 & 372.567691& 65.351523& 2.602873&  \textbf{133.165438} \\
      CSH &   289.067152& 381.593622& 67.613172& 2.175278& \textbf{4439.564212} \\
      DBF &   288.624437& 377.449849& 63.421812& 2.746393&  \textbf{888.773243} \\
      ENF &  288.183849& 377.676463& 61.559242& 4.015362&  \textbf{978.084845} \\
      GRA &  288.425651& 377.264645& 61.598768& 2.281074& \textbf{1141.630778} \\
      \hline
      \multicolumn{2}{l}{}
    \end{tabular}
  \end{table}
\end{frame}

\begin{frame}{Statistics with uncertainty}
  \scriptsize
  \begin{table}
    \caption{Statistics of $\frac{\partial \; ET}{\partial \; VPD}$ as a function of PFT.}
    \centering
    \begin{tabular}{l c c c c c}
      \hline
      PFT & $\overline{\frac{\partial \; ET}{\partial \; VPD}}$ & $\frac{\partial \; ET}{\partial \; VPD}\left(\overline{env}\right)$ & $\frac{\partial \; ET}{\partial \; VPD}\left(\overline{env}\right)*\text{std}(VPD)$ & $\frac{\frac{\partial \; ET}{\partial \; VPD}\left(\overline{env}\right)*\text{std}(VPD)}{ \frac{\partial \; ET}{\partial \; R}\left(\overline{env}\right)*\text{std}(R)}$ & fraction $\frac{\partial \; ET}{\partial \; VPD} < 0.$ \\
      \hline
      CRO & 0.000853 & 0.026241 & 37.05 & 0.41 & 0.473311\\
      CSH & -0.108234 & -0.091526 & 101.72 & 0.88 & 0.931660\\
      DBF & -0.012727 & 0.013794 & 39.47 & 0.33 & 0.461674\\
      ENF & -0.034087 & 0.000706 & 33.22 & 0.30 & 0.534425\\
      GRA & -0.019637 & -0.000921 & 33.60 & 0.35 & 0.631735\\
      \hline
      \multicolumn{2}{l}{}

    \end{tabular}
  \end{table}
\end{frame}
\begin{frame}{ideas}
  joint distributions of LAI and VPD, and RH and esat
  put vpd in kpa
  add pictures to first slide
\end{frame}

\begin{frame}{Scaling Term}
  \[\frac{\partial \;  ET}{\partial \; D} = \mathbf{ \frac{g_a \; P}{T(\Delta + \gamma)} }   \left(\frac{ c_p}{R_{air}} - \frac{\text{LAI$_{ref}$}}{\text{LAI}} \frac{\gamma c_s }{1.6 \; R*\; \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{D}}{2 (g_1 + \sqrt{D})^2}\right) \right)\]
  \begin{figure}
    \includegraphics[width=3.0in]{scaling.png}
    % \caption{}
  \end{figure}
\end{frame}

@@

\begin{frame}{How to take VPD derivative?}
  % below gnereated in fig03.py
  \includegraphics[width=3.0in]{e_s_rh.png}
\end{frame}

\begin{frame}{Is uncertainty a function of VPD?}
  \includegraphics[width=3.0in]{vpd_sigma.png}
\end{frame}
